Temporality of the Victorian Hospital Patient Transfer Network

### 2025-06-09 reports/diagrams/network_diags/temporal.tex
meaningless small updates

\node at (19.0,-15.0) [draw,solid,minimum width=1.6 cm,minimum height=1.6 cm,inner sep=0](A0){A};
\node at (19.0,-47.0) [draw,solid,minimum width=1.6 cm,minimum height=1.6 cm,inner sep=0](B0){B};
\node at (61.0,-15.0) [draw,solid,minimum width=1.6 cm,minimum height=1.6 cm,inner sep=0](A1){A};
\node at (61.0,-47.0) [draw,solid,minimum width=1.6 cm,minimum height=1.6 cm,inner sep=0](B1){B};

>>>>

\node at (19.0,-15.0) [draw,solid,minimum width=1.6 cm,minimum height=1.6 cm,inner sep=0](A0){$u_s$};
\node at (19.0,-47.0) [draw,solid,minimum width=1.6 cm,minimum height=1.6 cm,inner sep=0](B0){$v_s$};
\node at (61.0,-15.0) [draw,solid,minimum width=1.6 cm,minimum height=1.6 cm,inner sep=0](A1){$u_t$};
\node at (61.0,-47.0) [draw,solid,minimum width=1.6 cm,minimum height=1.6 cm,inner sep=0](B1){$v_t$};

### 2025-06-09 reports/paper.qmd
meaningless small updates

:::{.hidden}
$$
\newcommand{\dd}[2][t]{\frac{\mathrm{d}#2}{\mathrm{d}#1}}
\newcommand{\ceil}[1]{\lceil#1\rceil}
$$
:::

@@

@@

```{python}
#| label: compute-movement-over-time
base_date = datetime.date(2011, 1, 1)
aggregated_movement = pl.read_csv(root / "data/concordant_networks/analyses/movement_aggregated.csv")
aggregated_movement = (
  aggregated_movement
  .group_by('t')
  .agg(pl.col('w').sum())
  .sort('t')
  .with_columns(
    date=pl.lit(base_date) + pl.duration(days=pl.col('t')),
    my=pl.col('w').rolling_mean(window_size=365, center=True),
    mw=pl.col('w').rolling_mean(window_size=7, center=True),
    mm=pl.col('w').rolling_mean(window_size=28, center=True),
  )
)
```

```{python}
#| label: fig-movement-over-time
#| fig-cap: Number of patient transfers throughout the network increases over time. Right-hand end of data exhibits censoring behaviour, since we do not see long-terms readmissions beyond the end of the data observation period. We also observe seasonal behaviour (most visually obvious with periods of a year and a week), and consistent decreases of transfers during public holiday periods, especially at the end of the year.
fig = plt.figure()
ax = fig.add_subplot()
sns.despine(ax=ax)

@@

```{python}
histories = {
  dir.stem: np.loadtxt(dir/"hosp_presence.csv", delimiter=',')
  for dir in (root / "simulations/zero_sims_resized/" ).iterdir()
}
```
```{python}
#| label: fig-homeprop-heatmap
#| fig-cap: Distribution of the number of indivdiuals at home (not in the hospital system) over the duration of the simulation for each model type.

>>>>

@@

:::{#fig-specific-model-diagrams layout-ncol=2 layout-nrow=2 layout-valign="bottom"}

![Naïve static](diagrams/network_diags/naive_static.pdf)

![Static](diagrams/network_diags/static.pdf)

![Snapshot](diagrams/network_diags/snapshot.pdf)

![Temporal](diagrams/network_diags/temporal.pdf)

Schematic diagrams of each type of network representation for a two-facility network. Solid arrows represent direct transfers, dashed arrows represent indirect transfers, and wavy lines represent temporal consistency.
:::

@@

```{python}
#| label: compute-movement-over-time
base_date = datetime.date(2011, 1, 1)
aggregated_movement = pl.read_csv(root / "data/concordant_networks/analyses/movement_aggregated.csv")
aggregated_movement = (
  aggregated_movement
  .group_by('t')
  .agg(pl.col('w').sum())
  .sort('t')
  .with_columns(
    date=pl.lit(base_date) + pl.duration(days=pl.col('t')),
    my=pl.col('w').rolling_mean(window_size=365, center=True), # yearly ma
    mw=pl.col('w').rolling_mean(window_size=7, center=True), # weekly ma
    mm=pl.col('w').rolling_mean(window_size=28, center=True), # monthly ma
  )
)
```

```{python}
#| label: fig-movement-over-time
#| fig-cap: Number of patient transfers throughout the network increases over time. Moving averages plotted in red with periods of 1 year (main plot) and 1 week (inset). Right-hand end of data exhibits censoring behaviour, since we do not see long-terms readmissions beyond the end of the data observation period. We also observe seasonal behaviour (most visually obvious with periods of a year and a week), and consistent decreases of transfers during public holiday periods, especially at the end of the year.
fig = plt.figure()
ax = fig.add_subplot()
sns.despine(ax=ax)

@@

```{python}
#| label: compute-load-hosp-presence
histories = {
  dir.stem: np.loadtxt(dir/"hosp_presence.csv", delimiter=',')
  for dir in (root / "simulations/zero_sims_resized/" ).iterdir()
}
```
```{python}
#| label: fig-homeprop-heatmap
#| fig-cap: Distribution of the number of indivdiuals at home (not in the hospital system) over the duration of the simulation for each model type.
